\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-27 paper/main.tex
.

We utilize the PhenomeNET ontology \citep{PhenomeNET2011}, an ontology
integrating ontologies such as the Human Phenotype Ontology
\citep{HPO2018}, Gene Ontology \cite{GOoriginal2000, GOrecent2020},
Mammalian Phenotype Ontology \citep{MP2009} and several others.  We
obtained side effects and their links to drugs from SIDER
\citep{SIDER}; SIDER contains side effects encoded using identifiers
from the MedDRA database \citep{MedDRA}. We mapped side effects to the
PhenomeNET ontology using the \textit{Phenomebrowser.net}, which
provides a SPARQL query endpoint for the mentioned resources. The overall structure is depicted in Supplementary Figure 1.

@@

\subsubsection{Combined prediction model}
Combining half-twin and graph convolutional neural networks, we map
all protein representations to their respective node features,
initializing the graph convolutional update steps. The resulting
representations are used for a similarity prediction.
% as presented in
% figure ~\ref{fig:HalfTwinNetwork}
When combining ontology and molecular features with or without the
graph model, we concatenate both protein features and both drugs
features, before plugging them into the graph model for the similarity
computation. An overview of the model architecture, combining both
feature types, is shown in Supplementary Figure
4. Here
the original representations are transformed by a dense layer and then
used as input of a stack (with height 3) of residual graph
convolutional blocks. The full eventual model of \name{} is shown in Supplementary Figure 4.

>>>>

We utilize the PhenomeNET ontology \citep{PhenomeNET2011}, an ontology
integrating ontologies such as the Human Phenotype Ontology
\citep{HPO2018}, Gene Ontology \cite{GOoriginal2000, GOrecent2020},
Mammalian Phenotype Ontology \citep{MP2009} and several others.  We
obtained side effects and their links to drugs from SIDER
\citep{SIDER}; SIDER contains side effects encoded using identifiers
from the MedDRA database \citep{MedDRA}. We mapped side effects to the
PhenomeNET ontology using the \textit{Phenomebrowser.net}, which
provides a SPARQL query endpoint for the mentioned resources. The
overall structure is shown in Supplementary Figure 1.

@@

\subsubsection{Combined prediction model}
Combining half-twin and graph convolutional neural networks, we map
all protein representations to their respective node features,
initializing the graph convolutional update steps. The resulting
representations are used for a similarity prediction.
% as presented in
% figure ~\ref{fig:HalfTwinNetwork}
When combining ontology and molecular features with or without the
graph model, we concatenate both protein features and both drugs
features, before plugging them into the graph model for the similarity
computation. % An overview of the model architecture, combining both
% feature types, is shown in Supplementary Figure
% 4. 
Here the original representations are transformed by a dense layer and
then used as input of a stack (with height 3) of residual graph
convolutional blocks. The full model of \name{} is shown in
Supplementary Figure 4.
